\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-05-25 Report/notes.tex
ajout de courbe

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/sspqueue.png}
		\caption{The blue line is the result without phase type fitting.}
		\label{fig:res1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_01}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using hybrid engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_hybrid_01}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_001}
	\end{figure}

>>>>

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/ssp_hybrid.png}
		\caption{The blue line is the result without phase type fitting.}
		\label{fig:ssp_hybrid}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/distance_explicit.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_001}
	\end{figure}
